A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-09 papers/publication/paper-pollard.tex
msc

\begin{document}
\title{A Comparison of Parallel Graph Processing Benchmarks}
\author{Samuel D. Pollard \and Boyana Norris}
\institute{University of Oregon \\
	Eugene OR 97403, USA \\
	\email{\{spollard,norris\}@cs.uoregon.edu}
}
\maketitle
\begin{abstract}
There are an intimidating number of parallel graph processing systems. One survey in 2014 identified over 80. Since then, the landscape has changed; some packages have become inactive, even more have been introduced, and previous top performers have been usurped. To address the high churn of projects and the complexity of selecting a system for a given problem, we analyze the performance and scalability of four parallel open source graph processing systems (GraphMat, GAP Benchmark Suite, GraphBIG, and PowerGraph) using synthetic and real-world datasets. We perform analysis for three algorithms: breadth first search, single source shortest paths, and PageRank. We then compare our results to the most comprehensive parallel graph processing performance and benchmarking project: Graphalytics. We examine previously overlooked aspects of parallel graph processing performance such as energy usage in addition to a performance analysis model based on the Graph500.
\end{abstract}

>>>>

\begin{document}
\title{A Comparison of Parallel Graph Processing Benchmarks}
\author{Samuel D. Pollard \and Boyana Norris}
\institute{University of Oregon \\
	Eugene OR 97403, USA \\
	\email{\{spollard,norris\}@cs.uoregon.edu}
}
\maketitle
\begin{abstract}
The increasing popularity of large network analysis problems has led to the emergence of many parallel and distributed graph processing systems (one survey in 2014 identified over 80). Since then, the landscape has evolved---some packages have become inactive while others are being added. The challenge of trying to determine the best approach for a given problem is infeasible for most developers. To enable \emph{easy}, \emph{rigorous} and \emph{repeatable} comparison of parallel graph software capabilities, we have developed an approach and associated software for analyzing the performance and scalability of parallel open source graph processing systems.  We demonstrate our approach on four graph frameworks: GraphMat, GAP Benchmark Suite, GraphBIG, and PowerGraph using synthetic and real-world datasets. We analyze three algorithms: breadth first search, single source shortest paths, and PageRank and compare our results to Graphalytics. We examine previously overlooked aspects of parallel graph processing performance such as energy usage.
\end{abstract}
